---
title: "R Notebook"
output: html_notebook
---

# Introduction

In this study, I've chosen to examine the data on fraudulent online payment transactions. Visit <https://www.kaggle.com/datasets/jainilcoder/online-payment-fraud-detection> to access the information. Building a model that can identify fraudulent transactions is the aim of this project. Utilizing the ROC curve, also known as the Receiver Operating Characteristic, I will be using the machine learning model Logistic Regression to compare their accuracy. We start by importing the required libraries and loading the dataset's data.

# Importing the libraries
```{r}
library(dplyr)
library(caret) 
library(caTools)
library(data.table)
library(ggplot2)    
library(corrplot)
library(pROC)
```

# Importing the dataset

```{r}
dataset <- setDT(read.csv("D:/1st Sem-LTU 2022/online_fraud.csv"))
```

# Data Exploration

```{r}
head(dataset)
```
```{r}
summary (dataset)
```


```{r}
table(dataset$isFraud)
```

```{r}
names(dataset)
```
```{r}
summary(dataset$amount)
```

```{r}
hist(dataset$amount)
```
```{r}
hist(dataset$amount[dataset$amount < 100])
```
```{r}
colSums(is.na(dataset))
```
```{r}
head(dataset, 10)
```

# Data Visualization

```{r}
dataset %>%
  ggplot(aes(x = step, fill = factor(isFraud))) + 
  geom_histogram(bins = 100) + 
  labs(x = "Time elapsed since first transcation (hours)", y = "no. of transactions", title = "Distribution of transactions across time") +
  facet_grid(isFraud ~ ., scales = 'free_y') + theme()
```


```{r}
dataset %>% ggplot(aes(x=type, fill = type)) +
  geom_bar() + labs(title = "Transactions as per Type",  x = 'Transaction Type' , y = 'No of transactions' ) +  theme_classic()
```

```{r}
fraud_trans <- dataset %>% group_by(type) %>% summarise(fraud_transactions = sum(isFraud))

ggplot(fraud_trans, aes(x = type,  y = fraud_transactions)) +
  geom_col(aes(fill = 'type'), show.legend = FALSE) +
  labs(title = 'Fraud transactions as Per type', x = 'Transcation type', y = 'No of Fraud Transactions') +
  geom_text(aes(label = fraud_transactions), size = 4, hjust =.5) +
  theme_classic()
```

```{r}
ggplot(dataset[dataset$isFraud==1, ], aes(x = amount,  fill = amount)) +
  geom_histogram(bins = 40, aes(fill = 'amount')) +
  labs(title = 'Fraud transaction Amount distribution', y = 'No. of Fraud transacts', x = 'Amount in BDT')
```

```{r}
ggplot(dataset[dataset$isFraud==0,], aes(x = type, y = log(amount), fill = type)) +
  geom_boxplot(show.legend = FALSE) +
  labs(title= 'amount- boxplot' , x = 'types') +
  theme_classic()
```


```{r}
head(dataset, 5)
```

```{r}
library(gridExtra)
```

```{r}
origBal <- ggplot(dataset, aes(x = factor(isFraud), y = log1p(oldbalanceOrg), fill = factor(isFraud))) +
            geom_boxplot(show.legend = FALSE) +
            labs(title= 'Old balance in Origin Accounts', x = 'isFraud') +
            theme_classic()

destBal <- ggplot(dataset, aes(x = factor(isFraud), y = log1p(oldbalanceDest), fill = factor(isFraud))) +
            geom_boxplot(show.legend = FALSE) +
            labs(title= 'Old balance in Destination Accounts' , x = 'isFraud') +
            theme_classic()

grid.arrange(origBal, destBal, nrow = 1)
```

# Data Preprocessing


```{r}
df <- dataset %>% select(-c(nameOrig, nameDest, isFlaggedFraud))
```

```{r}
df
```
```{r}
df$amount <- scale(dataset$amount)
df_new <- df[, -c(1)]
head(df_new)
```


```{r}
df_new$isFraud <- as.factor(df_new$isFraud)
levels(df_new$isFraud) <- c("0", "1")
```

#Data Modeling

```{r}
set.seed(101)
split <- sample.split(df_new$isFraud, SplitRatio = 0.8)
train_data <- subset(df_new, split == TRUE)
test_data <- subset(df_new, split == FALSE)
dim(train_data)
```

```{r}
dim(test_data)
```
```{r}
library(ROSE)
```

```{r}
set.seed(90)
up_train_data <- upSample(x = train_data[, -7],
                         y = train_data$isFraud)
table(up_train_data$isFraud)
```


# Logistic Regression

```{r}
logistic_model = glm(isFraud~., train_data, family = binomial())

```

```{r}
summary(logistic_model)
```

```{r}
plot(logistic_model)
```




```{r}
logit = glm (isFraud ~., family = binomial(), data = df_new)
logit.prob = predict(logit, type = 'response')
logit.class = ifelse (logit.prob > 0.5, '1', '0') %>% as.factor()
c_m = table (df_new$isFraud, logit.class)
c_m

```

# Ploting ROC-AUC Curve

```{r}
library(pROC)
```
```{r}
logistic_predictions <- predict(logistic_model, test_data, type='response')
roc.curve(test_data$isFraud, logistic_predictions, plotit = TRUE, col = "blue")
```



















